---
title: "Individual 2: Christian Simmons"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")   

head(choco)

```
1. How are ratings distributed? Don’t forget to mention outliers, if there are any:

```{r}
boxplot(choco$Rating,xlab="Ratings of Chocolate")
```

It seems like the ratings have more outliers toward the bottom of the spectrum with a couple around the top, but most ratings are right around 3.2 in what looks to be a mostly normal distribution.

2. Do ratings depend on the cacao percentage of a chocolate bar?
```{r}
ratingRound <- round(choco$Rating)
counts <- table(ratingRound, choco$Cocoa.Pct)
barplot(counts, main="Car Distribution by Gears and VS",
  xlab="Cocoa Percent", col=c("darkblue","red","yellow","light green","pink"),
  legend = rownames(counts))
```

Most of the 5 and 4 stars seem to be around the 70% Cocoa range.

3. What class is the variable representing company locations? How is this different from a ‘character’ variable? (You do not need to produce a graphic for this question.)

```{r}
class(choco$Broad.Bean.Origin)
```
The variable is a "factor" class variable. This means the characters in the string are stored as integers instead of characters. This can be useful for keeping file size low.